---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# econdatasets

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/econdatasets)](https://cran.r-project.org/package=econdatasets)
[![CRAN downloads](https://cranlogs.r-pkg.org/badges/econdatasets)](https://cran.r-project.org/package=econdatasets)
![R CMD Check](https://github.com/tidy-intelligence/r-econdatasets/actions/workflows/R-CMD-check.yaml/badge.svg)
![Lint](https://github.com/tidy-intelligence/r-econdatasets/actions/workflows/lint.yaml/badge.svg)
[![Codecov test coverage](https://codecov.io/gh/tidy-intelligence/r-econdatasets/graph/badge.svg)](https://app.codecov.io/gh/tidy-intelligence/r-econdatasets)
<!-- badges: end -->

The 'EconDataverse' is a universe of open-source packages to work seamlessly with economic data. This package is designed to make it easy to download selected datasets that are preprocessed by 'EconDataverse' packages and publicly hosted on 'Hugging Face'. Learn more about the 'EconDataverse' at [econdataverse.org](https://www.econdataverse.org). 

## Installation

You can install `econdatasets` from [CRAN](https://cran.r-project.org/package=econdatasets) via:

``` r
install.packages("econdatasets")
```

You can install the development version of `econdatasets` from [GitHub](https://github.com/tidy-intelligence/r-econdatasets) with:

``` r
# install.packages("pak")
pak::pak("tidy-intelligence/r-econdatasets")
```

## Usage

```{r}
library(econdatasets)
```

Use `ed_get()` to load a specific table from a dataset:

```{r example}
counterparts <- ed_get("wbids", "counterparts")
head(counterparts, 5)
```

Use `ed_get_tables()` to see all tables available in a specific dataset:

```{r}
ed_get_tables("imfweo")
```

Use `ed_get_datasets()` to view all published datasets:

```{r}
ed_get_datasets()
```

If you miss a specific datasets, please consider opening an issue with your request. 

## Contributing

Contributions to `econdatasets` are welcome! If you'd like to contribute, please follow these steps:

1. **Create an issue**: Before making changes, create an issue describing the bug or feature you're addressing.
2. **Fork the repository**: After receiving supportive feedback from the package authors, fork the repository to your GitHub account.
3. **Create a branch**: Create a branch for your changes with a descriptive name.
4. **Make your changes**: Implement your bug fix or feature.
5. **Test your changes**: Run tests to ensure your changes don't break existing functionality.
6. **Submit a pull request**: Push your changes to your fork and submit a pull request to the main repository.